\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-03 paper.qmd
Added S-curve best model
Added bad model for S-curve

>>>>

<!--langevitour with best pD model for S-curve-->
::: {#fig-scurve_sc layout-ncol="3" fig-pos="H"}
![](figures/scurve/sc_best_1.png)

![](figures/scurve/sc_best_2.png)

![](figures/scurve/sc_best_3.png)

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/4RFNENX_fXk>).
:::

<!--langevitour with bad pD model for S-curve-->
::: {#fig-scurve_sc layout-ncol="3" fig-pos="H"}
![](figures/scurve/sc_bad_1.png)

![](figures/scurve/sc_bad_2.png)

![](figures/scurve/sc_bad_3.png)

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/DHPvhkZ0lUM>).
:::

### 2024-06-03 paper.tex
Added bad model for S-curve

>>>>

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_1.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_2.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_3.png}\end{minipage}%

\caption{\label{fig-scurve_sc}Screen shots of the \textbf{langevitour}
of the S-curve, shows the model-in-data space, a video of the tour
animation is available at (\url{https://youtu.be/DHPvhkZ0lUM}).}
